### 2019-02-21 sections/relatedwork.tex
add something about mtasks to related work

\paragraph{mTasks}
\fixme{Hier iets gezelligs over mTasks}

@@

% mTasks is another implementation of TOP, designed for coordination of IoT devices. \alert{cite MSc Lubbers}
% mTasks has been used in a demonstrator for home automation. \alert{cite MSc Andrade}

>>>>

@@

\paragraph{mTasks}

The \MTASKS framework is an implementation of \TOP geared towards \IOT devices.
As \TOPHAT its basic combinators are a subset of \ITASKS.
They are similar to those of \TOPHAT.
However, on \IOT devices it is useful to continue running tasks endlessly,
which is done in \MTASKS using a \CL{forever} combinator.
This is currently not possible in \TOPHAT.

As for \ITASKS, there is currently no formal semantics for \MTASKS.
